A Triple Origin for Twin Blue Stragglers in Compact Binaries

### 2018-12-11 BSS7782.tex
Added Lagrangian radii figure

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_t600_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
\caption{Same as Fig.\,\ref{fig:topview_at_t0} but at an age of $t
  \simeq 996days$.
\label{fig:topview_at_t1000day}}
\end{figure}

>>>>

\begin{figure}[ht!]
  \includegraphics[width=0.49\columnwidth]{lagrange_points_and_sph.pdf}
~  \includegraphics[width=0.51\columnwidth]{fig_t600_N80000_M012MSun1109MSun_a02au_e00_inc9deg.pdf}
\caption{Same as Fig.\,\ref{fig:topview_at_t0} but at an age of $t
  \simeq 996days$. Left panel shows the equipotential surface of the
  triple overplotted with the gas distribution, the right panel shows
  just the gas and the stars as bullets.
\label{fig:topview_at_t1000day}}
\end{figure}
